---
title: "Data Product week 2 Asignment"
author: "Sarah R"
date: "18/09/2017"
output: ioslides_presentation
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

## Human Development data

The United Nations Development Programme publishes data on Human Development Index (HDI) and poverty. Here we want to represent the countries in the world on a map alongside their ranking.  For more details on the data source see <http://hdr.undp.org/en>.

```{r ind, echo = T}
setwd("/Users/srieubland/Documents/Documents/DataScience/09_DataProduct/week2/asignment")
dfIndex <- read.csv("Poverty.csv", stringsAsFactors = F, 
                    header = T, skip = 1)
```

Some minimal cleansing of the Country names.
```{r ind2, echo = T}
dfIndex[46,]$Country <- "  Cote d'Ivoire"
dfIndex$Country <- substr(dfIndex$Country,2, nchar(dfIndex$Country))
```

## Coordinates of countries

In order to plot the countries on the map, we download data on the average latitude and longitude for each country, from the opendata on Socrata.com (<https://opendata.socrata.com/>)

```{r coord, echo = T, cache = T}
fileUrl2 <- "https://opendata.socrata.com/api/views/mnkm-8ram/rows.csv?accessType=DOWNLOAD"
download.file(fileUrl2,destfile = "coordinates.csv",method = "curl")
dateDownloaded <- date()
```

We downloaded the dataset on `r dateDownloaded`. We match the country name and transfer the coordinates

```{r coord2, echo = T}
dfCoord <- read.csv("coordinates.csv", stringsAsFactors = F)
dfIndex$latitude <- dfCoord[match(dfIndex$Country, dfCoord$Country),]$Latitude..average.
dfIndex$longitude <- dfCoord[match(dfIndex$Country, dfCoord$Country),]$Longitude..average.
```

## Prepare the Leaflet Map

We prepare the pop-up names to display on the Leaflet map.
```{r prep, echo = TRUE}
dfIndex$name <- paste0(dfIndex$Country, " - Ranking = ", dfIndex$HDI.Rank..2015.)
dfIndex2 <- dfIndex[!is.na(dfIndex$lat), c("name", "latitude", "longitude")]
```

We display the world map with Leaflet and include markers with pop-up windows showing the name of the country and the HDI Ranking.
```{r prep2, echo = TRUE, eval = F}
library(leaflet)
dfIndex2 %>% 
        leaflet() %>%
        addTiles() %>%
        addMarkers(popup = dfIndex2$name)
```

## Countries by HDI ranking (2015)

```{r map, echo = F, message= F}
library(leaflet)
dfIndex2 %>% 
        leaflet() %>%
        addTiles() %>%
        addMarkers(popup = dfIndex2$name)
```

